Blum axioms and nondeterministic computation of functions

### 2016-01-07 paper.tex
paper.tex: Promote the subsection about Blum axioms to a section.
paper.tex: Add sketch for introduction.

@@

\subsection{Blum axioms}
\label{sec:blum-axioms}

>>>>

Theory of Computation is mostly concerned about models of computation.
In general, for each model of computation,
there is some standard mathematical ``procedure''
for finding the language associated with a device
(one instance of the model).
This fixation with languages has many nice features;
for example,
we have the duality between recognizers and generators.
We may even go further and identify the concept of ``model of computation''
with the task of representing an infinite language
with some finite amount of information.
This provides a simple way of comparing the relative power of two models of computation:
just see ``how many languages'' each model can represent
--- the one with ``more'' languages ``win''\footnote{
    That is,
    if every language that can be represented with a given model of computation $A$
    can also be represented with a given model $B$,
    but there are languages representable in $B$ that are not representable in $A$,
    we say that $B$ is more \emph{powerful} or \emph{expressive} than $A$.
    $A$ and $B$ are said to be \emph{equivalent}
    if every language representable in $A$ is representable in $B$ and vice versa.
}.

Most problems need to be adapted to languages
in order to discuss its representability.

@@

\section{Blum axioms}
\label{sec:blum-axioms}
